---
title: 'RMarkdown:  In Class Assignment'
author: "Fredy Guevara"
date: "Data 2401"
output: 
  html_document:
    toc: TRUE
    toc_depth: 3
---


```{r setup, include=FALSE}
# Everything in this chunk is R code. 
# You are not expected to understand or edit this yet. 
# We will talk about what this does in a later class, with a little preview in part 2.
knitr::opts_chunk$set(echo = TRUE) 
```


Reminders: 

- You do not need to memorize Markdown syntax.
- You are expected to look things up using:
   - RStudio’s Markdown Help
   - Online documentation or examples
- Click Knit as you go to check that your document still renders correctly.
- Commit at the end, but consider committing as you go as well. 



# Part 1: Markdown Practice

**Do not skip reading this instruction** Create a new section at the end of this section named "Your work here". In that section, complete the tasks below:

- Make a *subsection* called Wise Words. 
- Put your favorite quote in a block quote. 
- Add a working, clickable link to a website that provides more information about that quote.
- Make another *subsection* called "I recommend", and add some information about your favorite author or musician: 
  - A _subsubheading_ with the name of the artist or author;    
  - An example of their writing or lyrics (formatted in a *block of text*);   
  - A _list_ of things they have written or performed (remember to use the formatting markup for a list!), with any of the titles/names in bold.     

# Part 2: Code Chunks

```{r echo = FALSE}
2 + 2
```

Complete the following steps:

- Knit the document and observe what appears in the output.
- Change the chunk option echo=TRUE to echo=FALSE.
- Knit the document again.
- Finally, write 2–3 sentences answering the following questions:
  - What changed between the two outputs?
  - Did the calculation still run when the code was hidden?
  - Why might someone want to hide code in a report?
  - Why might someone want to show code in a report?
  
# Part 3: A small R-in-markdown preview

- Create a subsection within this section called About this document.
- Write 2–3 sentences describing what this document is and what it produces.
- Include one value generated by inline R code.

> To include inline code, use this weird little `r 2+2` pattern, putting the code where I have 2+2 (which is code!) 
> You can use the function `Sys.Date()`, which would be added like this `r Sys.Date()` but you can do something else if you want. (Look at the knit html to see what this does.)



 

# Submitting Instructions

When you are finished: 

- Knit the document so that it produces an html file.
- Stage, commit, and push:
  - The updated `.rmd` file 
  - The generated `.html` file
- Submit the GitHub link to the assignment on Canvas.

# Fredy Work Here
## Wise Words

> “No one is born into this world to be alone!” - Jaguar D. Saul

[Best One Piece Quotes](https://www.crunchyroll.com/news/features/2025/5/12/one-piece-quotes?srsltid=AfmBOop-9xQuXAhWSFbMjYJK-4K8gr3FyU0A3Z1idNe1Numjjww5-Phc)

[Jaguar D. Saul](https://onepiece.fandom.com/wiki/Jaguar_D._Saul)

## I recommend
### Echiro Oda

````
Pirates are Evil? Marines are righteous? These terms have always changed throughout the course of history. Kid's who have never seen peace and kid's who have never seen war have different values! Those who stand at the top determine what's wrong and what's right! This very place is a neutral ground! Justice will prevail you say, of course it will. Those who win the war, become the Justice.
````

- **One Piece**

## Part 2 Work

What changed between the the two outputs when I changed it from true to false was whether the 2 + 2 was hidden or not. The code still ran the same and I believe people would like code hidden in many instances as they just want the results.As for wanting to have the code be shown in reports a reason I could see is that the person wants their work shown so others could understand the process or what was done to achieve the said result.

## About this document

This document is supposed to show my mastery of r by showing how I can format text differently. It is supposed to be practice for me and classwork at the same time. It should produce a text document or html that is formatted correctly.
`r Sys.Date()`
`r 33+34 ` 